\documentclass[journal]{IEEEtran}

\usepackage{cite}

\ifCLASSINFOpdf
\usepackage[pdftex]{graphicx}
\else
\fi

\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{algorithm, algorithmic}
\usepackage{array}
\usepackage{multirow}


\ifCLASSOPTIONcompsoc
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
\usepackage[caption=false,font=footnotesize]{subfig}
\fi

\usepackage{url}
\usepackage{booktabs}


% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}


\newcommand{\xj}[1]{\textcolor[rgb]{1,0,0}{(#1)}}
\newcommand{\zj}[1]{\textcolor[rgb]{1,0,1}{(#1)}}
%\newcommand{\md}[1]{\textcolor[rgb]{0,0,1}{#1}}
\newcommand{\td}[1]{\textcolor[rgb]{0.5,0.0,0.5}{#1}}

\newcommand{\blk}{\mathbf{B}}
\newcommand{\nrt}{N}
\newcommand{\nset}{\mathcal{N}}
\newcommand{\brc}{F}
\newcommand{\delete}[1]{}

\usepackage[pagebackref=false,breaklinks=false,letterpaper=false,colorlinks,bookmarks=false]{hyperref}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
%\title{Progressive Learning for Neuronal Population\\ Reconstruction from Optical Microscopy Images}
%\title{Unsupervised Progressive Learning for Neuronal Population Reconstruction from Ultra-scale\\ 3D Optical Microscopy Images}
\title{Neuronal population reconstruction from ultra-scale optical microscopy images via progressive learning}
% 
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%\ifCLASSOPTIONpeerreview
\author{Jie Zhao, Xuejin Chen, Zhiwei Xiong, Dong Liu, Junjie Zeng, \\Yueyi Zhang, Zheng-Jun Zha, Guoqiang Bi, \and Feng Wu
\thanks{This work was supported by the Natural Science Foundation of China under Grant 61632006 and 91732304, and the Fundamental Research Funds for the Central Universities under Grant WK2380000002 and WK3490000003.}
%\thanks{J. Zhao, X. Chen, Z. Xiong, D. Liu, J. Zeng, C. Xie, Y. Zhang, Z. Zha, and F. Wu are with the CAS Key Laboratory of Technology in Geo-spatial Information Processing and Application System, EEIS Department, University of Science and Technology of China, Hefei 230027, China (email: \{jzhaoch, artzjj, xcy12345\}@mail.ustc.edu.cn; \{xjchen99, zwxiong, dongeliu, zhyuey, zhazj, fengwu\}@ustc.edu.cn).}
%xjchen99@ustc.edu.cn; zwxiong@ustc.edu.cn; dongeliu@ustc.edu.cn; zhyuey@ustc.edu.cn; zhazj@ustc.edu.cn; fengwu@ustc.edu.cn).}
%\thanks{G. Bi is with CAS Key Laboratory of Brain Function and Disease, and School of Life Sciences, University of Science and Technology of China, Hefei 230027, China (email: gqbi@ustc.edu.cn).}
\thanks{J. Zhao, X. Chen, Z. Xiong, D. Liu, J. Zeng, Y. Zhang, Z. Zha, G. Bi and F. Wu are with the National Engineering Laboratory for Brain-inspired Intelligence Technology and Application, University of Science and Technology of China, Hefei 230027, China (email: \{jzhaoch, artzjj\}@mail.ustc.edu.cn; \{xjchen99, zwxiong, dongeliu, zhyuey, zhazj, gqbi, fengwu\}@ustc.edu.cn).}
}
%\fi
% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.



% The paper headers
\ifCLASSOPTIONpeerreview
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
\fi
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.




% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.



% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}


% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Reconstruction of neuronal populations from ultra-scale optical microscopy (OM) images is essential to investigate neuronal circuits and brain mechanisms.
The noises, low contrast, huge memory requirement and high computational cost pose significant challenges in the neuronal population reconstruction.
%
Recently, many studies have been conducted to extract neuron signals using deep neural networks (DNNs).
However, training such DNNs usually relies on a huge amount of voxel-wise annotations in OM images, which are expensive in terms of both finance and labor.
%Moreover, the high memory cost of DNNs limits the volume of input images that can be handled at one time. 
%
In this paper, we propose a novel framework for dense neuronal population reconstruction in ultra-scale images.
%
To solve the problem of high cost in obtaining manual annotation for training DNNs, we propose a progressive learning scheme for neuronal population reconstruction (PLNPR) which does not require any manual annotations. 
%
Our PLNPR scheme consists of a traditional neuron tracing module and a deep segmentation network that mutually complement and progressively promote each other. 
%Based on the DNN model progressively trained, reconstructing neurons from local noisy image blocks is feasible with allowed memory.
%
To reconstruct dense neuronal populations from a terabyte-sized ultra-scale image, we introduce an automatic framework which adaptively traces neurons block by block and fuses multiple neurons in overlapped regions continuously and smoothly.
%
We build a dataset ``VISoR-40" which consists of 40 large-scale OM image blocks from cortical regions of a mouse.
Extensive experimental results on our VISoR-40 dataset and the public BigNeuron dataset demonstrate the effectiveness and superiority of our method on neuronal population reconstruction and single neuron reconstruction.
Furthermore, we successfully apply our method to reconstruct dense neuronal populations from an ultra-scale mouse brain slice. 
The proposed adaptive block-wise reconstruction and fusion strategy greatly improve the completeness of neurites in dense neuronal population reconstruction. 
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Neuronal population reconstruction, ultra-scale images, optical microscopy, progressive learning.
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
%\IEEEpeerreviewmaketitle


%%%%%%%%% BODY TEXT
\input{intro}
\input{relatedwork}
\input{algorithm}
\input{results}

%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:conclusion}
In this work, we propose PLNPR, a progressive learning framework for neuronal population reconstruction from noisy and low-quality OM image blocks.
Without using any manual annotations, our PLNPR method takes advantage of neuron tracing techniques and deep segmentation networks, and makes them mutually complement and promote each other progressively.
We extensively validate the proposed PLNPR for neuron reconstruction and the results demonstrate the effectiveness and superiority of our method.
Integrating PLNPR with an efficient block-wise tracing and fusion strategy, our UltraNPR successfully reconstruct dense neuronal populations from an ultra-scale OM images of a mouse brain slice.
%
We construct a new dataset ``VISoR-40'' which consists of 40 OM image blocks for evaluation of neuronal population reconstruction.
This dataset is now available and we believe that it will facilitate further brain studies, including neuron counting, neuron reconstruction, neuron morphology analysis, and so on.

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%


%\input{appendices}


% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi



% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section
% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\bibliographystyle{IEEEtran}
\bibliography{NeuroSegRef}
% that's all folks
\end{document}